### 2020-12-16 README.Rmd
update README. Still working on this.

>>>>

# Usage

The workflow is going to look something like this.

```{r, cache=F, message=F}

library(tidyverse, quietly = TRUE)
library(peacesciencer)
library(tictoc)

tic()
create_dyadyears() %>%
  # Add Gleditsch-Ward codes
  add_gwcode_to_cow() %>%
  # Add capital-to-capital distance
  add_capital_distance() %>%
  # Add contiguity information
  add_contiguity() %>%
  # Add major power data
  add_cow_majors() %>%
  # Add democracy variables
  add_democracy() %>%
  # add alliance data from Correlates of War
  add_cow_alliance() %>%
  # you should probably filter to politically relevant dyads earlier than later...
  # Or not, it's your time and computer processor...
  filter_prd()
toc()

```
